Motorcycle Acceleration example

### 2018-10-10 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

Apply other methods to the Motorcycle Accident data
---------------------------------------------------

Apply Empirical Bayes thresholding to the Motorcycle Accident data set.

```{r run-tithresh}
res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc, y.ini.mc)
```

Apply Empirical Bayes thresholding to the Motorcycle Accident data,
this time using the variances estimated by SMASH.

@@

SUMMARIZE RESULTS FROM ALL METHODS
----------------------------------

Create another plot showing the Motorcycle Accident data and the
estimates provided by the four methods.

```{r}
plot(res.mc$x, res.mc$mu.est, type = 'l',
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
     xlab = "time (ms)", ylab = "acceleration (g)", lwd = 2)
lines(res.mc$x, res.mc$mu.est + 2 * sqrt(res.mc$var.est), col = 2,
      lty = 5, lwd = 1.8)
lines(res.mc$x, res.mc$mu.est - 2 * sqrt(res.mc$var.est), col = 2,
      lty = 5, lwd = 1.8)
lines(res.ti.cons.mc$x, res.ti.cons.mc$mu.est, lwd = 2, col = 4)
lines(res.cons.mc$x, res.cons.mc$mu.est, lwd = 2, col = 'brown')
lines(res.ti.mc$x, res.ti.mc$mu.est, lwd = 2, col = 'darkgreen')
points(res.mc$x, res.mc$y, cex = 0.7, pch = 16, col = alpha("black", 0.5))
legend('bottomright',
       legend = c('SMASH', 'SMASH, homo', 'TI-thresh, SMASH est',
                  'TI-EBthresh, homo'),
       lty = c(1, 1, 1, 1), lwd = c(2, 2, 2, 2),
       col = c(1, 'brown', 'darkgreen', 4))
```

>>>>

Apply TI thresholding to the Motorcycle Accident data
---------------------------------------------------

Apply TI thresholding to the Motorcycle Accident data set.

```{r run-tithresh}
res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
```

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated by SMASH.

@@

Compare results from all methods
--------------------------------

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted magenta line), TI thresholding (dark blue line), and TI
thresholding when the variances have been estimated by SMASH (dotted
green line).

```{r plot-all-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```
